Chapter 2 Figures

### 2019-12-23 doc/figureFiles/figures.Rmd
added more tick marks, changed axis title

Fig1_Bv2_strain <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain, color=strain, shape = sex))+
  #facet_grid(~sex, scales = "free", space="free")+ 
  ylab("Average MLH1 Foci per Cell")+
  geom_point(aes(shape = sex), size=3, position=position_dodge(.5))+

@@

  ylim(c(19.5, 33))+
 scale_color_manual(values=colors_of_strains)+ 
  #legend.position="none",
  theme(legend.position="bottom",legend.box = "horizontal",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+

>>>>

Fig1_Bv2_strain <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain, color=strain, shape = sex))+
  #facet_grid(~sex, scales = "free", space="free")+ 
  ylab("Number of Crossovers per Cell")+
  geom_point(aes(shape = sex), size=3, position=position_dodge(.5))+

@@

  ylim(c(19.5, 33))+
 scale_color_manual(values=colors_of_strains)+ 
  scale_y_continuous(breaks=seq(20,32,2) )+

  #legend.position="none",
  theme(legend.position="bottom",legend.box = "horizontal",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
